Scoring epidemiological forecasts on transformed scales

### 2023-06-28 second submission after review/reply_to_reviews.tex

\newcommand{\indented}{\setlength{\leftskip}{1cm}}
\newcommand{\notindented}{\setlength{\leftskip}{0cm}}

\begin{document}

%\black \textbf{Black: our comments}
%\red \textbf{Reviewer, not addressed}
%\blue \textbf{Reviewer, addressed}

\black
We thank the reviewers for their feedback and thoughtful comments which we feel have helped improve the manuscript substantially. Please see our responses to the individual comments as well as explanations on the changes we have made to the manuscript below. 
In addition to the changes outlined below we made some general edits to the paper. We changed the title to make it more concise, we altered the order of some sections and shortened the introduction a bit, which had after the revision had become somewhat long.

@@

\notindented

\blue
\subsubsection{Log vs other transformations}
The authors take the position that the log transformation is generally preferable for their use case, though they discuss and compare others. Relatedly, their arguments in terms of relative error also involve an essentially log-linear (i.e. log data + additive error) form which may be pragmatic but somewhat inelegant imo.

\black
In the theoretical part of the manuscript we simplify the equations by looking at the case of a single point forecast, rather than a probabilistic forecast that comes in the form of a predictive distribution. We feel this makes the discussion more intuitive. We want to emphasise that the log-linear error $\varepsilon^*$ is really the error that is measured by the score, not the error model that would be assumed by any forecaster making a prediction.

@@

\blue
As the authors note, a particularly controversial issue for the log transformation is the issue of zero values. They take the standard pragmatic stance that we can use log (eps + y) instead of log y in such cases. Many communities e.g. econometrics are vehemently opposed to this, preferring e.g. quasi-Poisson regression and robust standard errors in the context of estimation. While not completely opposed to log (eps + y) myself (I have used it too!) it makes me a bit uncomfortable I still can’t help but feel that something along the lines of e.g. logarithmic/quasi-likelihood or deviance scores could be formulated that would be preferable to the log data transform. This would offer both automatic scaling and handling of zero values, in principle. However, I haven’t thought carefully enough to offer a concrete alternative and the log(eps + y) approach appears to work reasonably here. Instead, and in combination with the previous point, perhaps a bit more discussion of the potential alternatives based on quasi-likelihood-style functions rather than data transformations could be added?

\black
Thank you for raising this interesting point. The log score is indeed an alternative which is scale-invariant under strictly monotonic transformations. We now mention this in the introduction and state that for the log score the question of which scale to evaluate forecasts on does not arise. In our understanding, a quasi-likelihood approach (as opposed to an actual likelihood approach as in the log score) may not actually be necessary as at least in theory full predictive distributions are to be evaluated. Developing further ideas based on some form of quasi-likelihood would likely require more in-depth investigation, which we feel is beyond the scope of the current paper.

@@

\blue
\subsubsection{Observation and process models}
The interpretation in e.g. 2.2 appears to essentially assume a deterministic process model and additive error on the log scale (multiplicative on the natural scale). Although more of a motivating heuristic than strict assumption, a deterministic process model based on a mean will not in general be the same as a stochastic process model, right? Perhaps a further caveat that this is a fairly simplistic motivating tool might be useful?

Furthermore, why not assume that the model mean (say the output of the deterministic model) defines e.g. the mean of something like a Poisson distribution (probably in overdispersed/quasi form)? or negative binomial? The potential use of these distributions is considered in later sections in the context of motivating variance transforms, but then would again seem to motivate a (quasi-)likelihood-style score beyond the approximate transforms (though with pros and cons in terms of robustness, applicability in the presence of partial information).

\black
It is important to note that the equations in 2.2 do not refer to any particular model used by a forecaster or any model that was fit to data. Rather, we define the instantaneous growth rate for a single realised epidemic and then show that scoring forecasts for that on the log scale equates to scoring a forecast of the average growth rate according to this definition (this is essentially the same argument as in the first comment of Section 1.1.2 above). The forecaster themselves who would make a forecast could assume any error model or model structure they like.

@@

\blue
\subsection{Major comments}

``Natural logarithm'', log1p, and log($a + x$) are conflated in several places, despite the discussion in Section 2.4 noting that this is an important distinction. The terminology should not be overloaded. (E.g., L20 ``Applying the log transformation''.)

\black
We changed ``Applying the log transformation'' to ``Applying a transformation of log($x + 1$)'' in L20 (in the abstract).

We slightly disagree with the notion that the terminology should not be overloaded. Not introducing another term for transformations of $\log_{e}(x + \varepsilon)$ makes the manuscript more readable and accessible to readers. In addition, our analyses suggest that adding a small offset does not make much of a difference in most practical applications. We nevertheless completely agree that this should be made clear to the reader and have added the following text:

@@

The assumption of a quadratic mean-variance relationship is not entirely arbitrary, but rather has a specific interpretation in the sense that it encodes the assumption that one can forecast the growth rate equally well regardless of the observed magnitude at the moment. In the manuscript, we state:

\indented
The assumption of a quadratic mean-variance relationship is closely linked to the aspects discussed in Sections 2.1 and 2.2. It implies that relative errors have constant variance and can thus be meaningfully compared across different targets. Also, it arises naturally if we assume that our capacity to predict the epidemic growth rate does not depend on the expected outcome, i.e. does not depend on the current phase of the epidemic or the order of magnitude of current observations.

\notindented

For a specific motivation in a simple branching process model please see our reply to comment ``L166'' below.

@@

When applying a transformation, the order of the operations matters, and applying a transformation after scores have been computed generally does not guarantee that the score remains proper. In the case of log transforms, taking the logarithm of the CRPS values, rather than scoring the log-transformed forecasts and data, results in an improper score. We illustrate this point using simulated data in Figure SI.1, where it can be seen that in the example overconfident models perform best in terms of the log WIS. We note that strictly speaking, re-scaling average scores by the average score of a baseline model or average scores across different models  to obtain skill scores likewise leads to improper scores \citep{gneitingStrictlyProperScoring2007}. The application of such skill scores, however, is established practice and considered largely unproblematic.

\notindented

\blue
L166: “a negative binomial distribution with size parameter $\theta$” — Is this realistic? If so, what’s the interpretation epidemiologically?

\black
This is an illustrative example and is not meant to be completely realistic. Rather, the point is to illustrate that for observations which have a standard deviation that grows linearly with the mean, the log transformation can serve as a variance-stabilising transformation. However, negative binomial distributions are commonly used in the epidmeiological literature; see e.g., Section 3 of Meyer and Held (2017, \url{http://dx.doi.org/10.1214/14-AOAS743}). An epidemiological interpretation could be the following (see e.g. Funk, Abbott and Bracher \url{https://doi.org/10.1111/rssa.12974}):
\begin{itemize}
    \item For simplicity assume a generation time of one time interval (this could be relaxed).
    \item Each of the $Y_{t - 1}$ infected individuals at time $t - 1$  generates new infections at time $t$, with a reproduction number of $R_t$ and independent Poisson offspring distributions. Assuming independence across infecting individuals and given $R_t$ and $Y_{t - 1}$, $Y_t$ then follows a Poisson distribution with mean $R_t \times Y_{t - 1}$.
    \item We assume that $R_t$ is not fixed, but given by
    $$
    R_t = R_0 \times \theta_t
    $$
    where
    $$
    \theta \sim \text{Gamma}(\text{shape} = \psi, \text{rate} = \psi).
    $$
    $R_t$ thus fluctuates around an average value of $R_0$.
    \item This implies
    $$
    Y_t \mid Y_{t - 1} \sim \text{NegBin}(\text{mean} = R_t \times Y_{t - 1}, \text{size} = \psi).
    $$
\end{itemize}
So a conditional negative binomial distribution with quadratic mean-variance relationship arises if we assume that a suitably distributed environmental factor $\theta_t$ modifies the reproductive number. While the assumption of this specific gamma distribution is arbitrary, a quadratic mean-variance relationship will also arise for other distributions of $\theta_t$.

@@

\blue
L24 “is only one” — Seems a bit too similar to “the only one”, “the only”, etc.

\black
We hope that the remainder makes it sufficiently clear that other transformations are possible.

\blue
L46 “WIS is an approximation of the CRPS” — Is it an approximation of CRPS itself or some (2x?) scaling?

\black
The weighted interval score is a weighted sum of interval scores for the individual prediction intervals. When weighing the individual interval scores for the central $1 - \alpha$ prediction intervals by 
$w = \alpha / 2$ (which is generally standard), then the WIS converges exactly to the CRPS for an increasing number of equally spaced prediction intervals. For an illustration see Figure 2 in the referenced paper by Bracher, Ray, Gneiting and Reich (2021).

@@

\notindented
\blue
L70: Clarify: is this suggesting to make the forecasting targets themselves the result of applying some standardized growth rate estimator to current+future observations around the desired time period?

\black 
Here we aren't suggesting a specific transformation yet, but rather just say that it would be desirable to score a forecast of the growth rate (regardless of how that can be achieved). Specific suggestions for how to achieve this (either by taking a log transformation or by using another transformation to obtain growth rates directly as mentioned in the Discussion) are discussed in more detail in the remainder of the text.

\blue
L99: How are atoms at $\exp x = 0$ handled? How are observations of $y = 0$ handled?

\black
In the theoretical discussion in Section 2 we defined prediction targets to have strictly positive support, so these cases are excluded. In the later parts we follow the common strategy to add an offset $a$ before taking the logarithm.

@@

\blue
4. Line 281: missing closing parenthesis, "(or $\beta_{\sqrt{}} = 0$, respectively".

\black
We corrected the typo

\blue
5. Figure 7: I can appreciate that the correlation between the natural and logarithmic scores decreases over the forecast horizon, as the absolute forecast error grows. But I found panel B more challenging to interpret. I gather the key message is that model rankings are quite consistent between the natural and log scales (panel A) even though the absolute scores differ markedly between the two scales — an effect that increases over the forecast horizon (panel B). Perhaps adding a sentence to this effect in the accompanying text (lines 292-295) would help other readers to avoid my confusion.

\black
You are right, we adapted the text and hopefully made it more clear:

### 2023-07-08 second submission after review/Manuscript-without-SI.tex
add tiff Figures for publication

\begin{figure}[h!]
\centering
\includegraphics[width = 1\textwidth]{output/figures/different-relative-errors.png}
\caption{Numerical comparison of different measures of relative error: absolute percentage error (APE), relative error (RE), symmetric absolute percentage error (SAPE) and the absolute error applied to log-transformed predictions and observations. We denote the predicted value by $\hat{y}$ and display errors as a function of the ratio of observed and predicted value. A: x-axis shown on a linear scale. B: x-axis shown on a logarithmic scale.}
\label{fig:SAPE}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/SIM-mean-state-size.png}
    \caption{Expected CRPS scores as a function of the mean and variance of the forecast quantity. We computed expected CRPS values  for three different distributions, assuming an ideal forecaster with predictive distribution equal to the true underlying (data-generating) distribution. 
    These expected CRPS values were computed for different predictive means based on 10,000 samples each and are represented by dots. Solid lines show the corresponding approximations of the expected CRPS from equations \eqref{eq:taylor_quadratic} and \eqref{eq:taylor_linear}. Figure \ref{fig:score-approx} shows the quality of the approximation in more detail. 
    The first distribution (red) is a truncated normal distribution with constant variance (we chose $\sigma = 1$ in order to only obtain positive samples). The second (green) is a negative binomial distribution with variance $\theta = 10$ and variance $\sigma^2 = \mu + 0.1\mu^2$. The third (blue) is a
    Poisson distribution with $\sigma^2 = \mu$. To make the scores for the different distributions comparable, scores were normalised to one, meaning that the mean score for every distribution (red, green, blue) is one. 
    A: Normalised expected CRPS for ideal forecasts with increasing means for three distribution with different relationships between mean and variance. Expected CRPS was computed on the natural scale (left), after applying a square-root transformation (middle), and after adding one and applying a log-transformation to the data (right). B: A but with x and y axes on the log scale.}
    \label{fig:SIM-wis-state-size-mean}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width = 1\textwidth]{output/figures/illustration-effect-log-ranking-crps.png}
\caption{Illustration of the effect of the log-transformation of the ranking for a single forecast. Shown are CRPS (or WIS, respectively) values as a function of the observed value for two forecasters. Model A issues a geometric distribution (a negative binomial distribution with size parameter $\theta = 1$) with mean $\mu = 10$ and variance $\sigma^2 = \mu + \mu^2 = 110$), while Model B issues a Poisson distribution with mean and variance equal to 10. Zeroes in this illustrative example were handled by adding one before applying the natural logarithm.}
\label{fig:illustration-ranking}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/HUB-model-comparison-ensemble.png}
    \caption{
    Forecasts and scores for two-week-ahead predictions from the EuroCOVIDhub-ensemble made in Germany. Missing values are due to data anomalies that were removed (see section \ref{sec:HUB-setting}. 
    A, E: 50\% and 90\% prediction intervals and observed values for cases and deaths on the natural scale. B, F: Corresponding scores. C, G: Forecasts and observations on the log scale. D, H: Corresponding scores. 
    }
    \label{fig:HUB-model-comparison-ensemble}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/HUB-mean-obs-location.png}
    \caption{Observations and scores across locations and forecast horizons for the European COVID-19 Forecast Hub data. Locations are sorted according to the mean observed value in that location. 
    A: Average (across all time points) of observed cases and deaths for different locations. B: Corresponding boxplot (y-axis on log-scale) of all cases and deaths. C: Scores for two-week-ahead forecasts from the EuroCOVIDhub-ensemble (averaged across all forecast dates) for different locations, evaluated on the natural scale as well as after transforming counts by adding one and applying the natural logarithm. D: Corresponding boxplots of all individual scores of the EuroCOVIDhub-ensemble for two-week-ahead predictions. E: Boxplots for the relative change of scores for the EuroCOVIDhub-ensemble across forecast horizons. For any given forecast date and location, forecasts were made for four different forecast horizons, resulting in four scores. All scores were divided by the score for forecast horizon one. To enhance interpretability, the range of visible relative changes in scores (relative to horizon = 1) was restricted to [0.1, 10].}
    \label{fig:HUB-mean-locations}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/HUB-scores-locations-log-variants.png}
    \caption{Mean WIS in different locations for different transformations applied before scoring. Locations are sorted according to the mean observed value in that location. Shown are scores for two-week-ahead forecasts of the EuroCOVIDhub-ensemble. On the natural scale (with no transformation prior to applying the WIS), scores correlate strongly with the average number of observed values in a given location. The same is true for scores obtained after applying a square-root transformation, or after applying a log-transformation with a large offset $a$. For illustrative purposes, $a$ was chosen to be 101630 for cases and 530 for deaths, 10 times the respective median observed value. For large values of $a$, $\log(x + a)$ grows roughly linearly in $x$, meaning that we expect to observe the same patterns as in the case with no transformation. For decreasing values of $a$, we give more relative weight to scores in small locations.}
    \label{fig:HUB-log-different-offsets}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/HUB-transformation-regression.png}
    \caption{Relationship between median forecasts and scores. Black dots represent WIS values for two-week ahead predictions of the EuroCOVIDhub-ensemble. Shown in red are the regression lines discussed in Section \ref{sec:HUB-regression} shown in Table \ref{tab:HUB-regression}. A: WIS for two-week-ahead predictions of the EuroCOVIDhub-ensemble against median predicted values. B: Same as A, with scores obtained after applying a square-root-transformation to the data. C: Same as A, with scores obtained after applying a log-transformation to the data.} 
    \label{fig:HUB-regression}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/HUB-correlations.png}
    \caption{Correlations of rankings on the natural and logarithmic scale. A: Average Spearman rank correlation of scores for individual forecasts. For every individual target (defined by a combination of forecast date, target type, horizon, location), one score was obtained per model. Then, for every forecast target, the Spearman rank correlation was computed between scores on the natural scale and on the log scale for all the models that had made a forecast for that specific target. These individual rank correlations were then averaged across locations and time and are displayed stratified by horizon and target types, representing average accordance of model ranks for a single forecast target on the natural and on the log scale. B: Correlation between relative skill scores. For every forecast horizon and target type, a separate relative skill score was computed per model using pairwise comparisons, which is a measure of performance of a model relative to the others for a given horizon and target type that accounts for missing values. The plot shows the correlation between the relative skill scores on the natural vs. on the log scale, representing accordance of overall model performance as judged by scores on the natural and on the log scale.}
    \label{fig:HUB-cors}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/HUB-pairwise-comparisons.png}
    \caption{Changes in model ratings as measured by relative skill for two-week-ahead predictions for cases (top row) and deaths (bottom row). A: Relative skill scores for case forecasts from different models submitted to the European COVID-19 Forecast Hub computed on the natural scale. B: Change in rankings as determined by relative skill scores when moving from an evaluation on the natural scale to one on the logarithmic scale. Red arrows indicate that the relative skill score deteriorated when moving from the natural to the log scale, green arrows indicate they improved. C: Relative skill scores based on scores on the log scale. D: Difference in relative skill scores computed on the natural and on the logarithmic scale, ordered as in C. E: Relative contributions of the different WIS components (overprediction, underprediction, and dispersion) to overall model scores on the natural and the logarithmic scale. F, G, H, I, J, K: Analogously for deaths.}
    \label{fig:HUB-rank-order}
\end{figure}

@@

\subsection{Alternative Formulation of the WIS}
\label{sec:alternative-wis}

Instead of defining the WIS as an average of scores for individual quantiles, we can define it using an average of scores for symmetric predictive intervals. For a single prediction interval, the interval score (IS) is computed as the sum of three penalty components, dispersion (width of the prediction interval), underprediction and overprediction,  
%
\begin{linenomath*}
\begin{align}
 IS_\alpha(F,y) &= (u-l) + \frac{2}{\alpha} \cdot (l-y) \cdot \boldsymbol{1}(y \leq l) + \frac{2}{\alpha} \cdot (y-u) \cdot \boldsymbol{1}(y \geq u) \\
 &= \text{dispersion} + \text{underprediction} + \text{overprediction},    
\end{align}
\end{linenomath*}
%
where $\boldsymbol{1}()$ is the indicator function, $y$ is the observed value, and $l$ and $u$ are the $\frac{\alpha}{2}$ and $1 - \frac{\alpha}{2}$ quantiles of the predictive distribution, i.e. the lower and upper bound of a single central prediction interval. For a set of $K^*$ prediction intervals and the median $m$, the WIS is computed as a weighted sum, 
\begin{linenomath*}
\begin{equation}
\text{WIS} = \frac{1}{K^* + 0.5} \cdot \left(w_0 \cdot |y - m| + \sum_{k = 1}^{K^*} w_k \cdot IS_{\alpha_{k}}(F, y)\right),    
\end{equation} 
\end{linenomath*}
where $w_k$ is a weight for every interval. Usually, $w_k = \frac{\alpha_k}{2}$ and $w_0 = 0.5$.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/example-log-first.png}
    \caption{Illustration of the effect of applying a transformation after scoring. We assume $Y \sim \text{LogNormal}(0, 1)$ and evaluate the expected CRPS for predictive distributions $\text{LogNormal}(0, \sigma)$ with varying values of $\sigma \in [0.1, 2]$. For the regular CRPS (left) and CRPS applied to log-transformed outcomes (middle), the lowest expectation is achieved for the true value $\sigma = 1$. For the log-transformed CRPS, the optimal value is  0.9, i.e. there is an incentive to report a forecast that is too sharp. The score is therefore no longer proper.}
    \label{fig:log-improper}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/illustration-effect-offset-log.png}
    \caption{Illustration of the effect of adding a small quantity to a value before taking the natural logarithm. For increasing x, all lines eventually approach the black line (representing a transformation with no offset applied).
    For a given solid line, the dashed line of the same colour marks the x-value that  is equal to 5 times the corresponding offset. It can be seen that for $a$ values smaller than one fifth of the transformed quantity, the effect of adding an offset is generally small. When choosing a suitable $a$, the trade-off is between staying close to the interpretation of a pure log-transformation (choosing a small $a$) and not giving excessive weights to small observations (by choosing a larger $a$, see Figure \ref{fig:HUB-log-different-offsets}).}
    \label{fig:illustration-effect-log-offset}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width = 1\textwidth]{output/figures/SIM-score-approximation.png}
\caption{
Visualisation of expected CRPS values against approximated scores using the approximation detailed in Section \ref{sec:methods:rankings} (see also Figure \ref{fig:SIM-wis-state-size-mean}). Expected CRPS scores are shown for three different distributions once on the natural scale (top row) and once scored on the log scale (bottom row).  
}
\label{fig:score-approx}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% HUB plots %

\begin{table}[h!]
    \centering
\begin{tabular}{lllcc}
\toprule
target type & quantity & measure & natural & log\\
\midrule
Cases & Observations & mean & 61979 & 9.19\\
Cases & Observations & sd & 171916 & 2.10\\
Cases & Observations & var & 29555122130 & 4.42\\
Deaths & Observations & mean & 220 & 3.89\\
Deaths & Observations & sd & 435 & 1.96\\
\addlinespace
Deaths & Observations & var & 189051 & 3.83\\
Cases & WIS & mean & 15840 & 0.27\\
Cases & WIS & sd & 53117 & 0.28\\
Deaths & WIS & mean & 31 & 0.23\\
Deaths & WIS & sd & 65 & 0.28\\
\bottomrule
\end{tabular}
    \caption{Summary statistics for observations and scores for forecasts from the ECDC data set.}
    \label{tab:HUB-summary}
\end{table}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/number-avail-forecasts.png}
    \caption{
    Number of forecasts available from different models for each forecast date. 
    }
    \label{fig:HUB-num-avail-models}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/number-anomalies.png}
    \caption{
    Number of observed values that were removed as anomalous. The values were marked as anomalous by the European Forecast Hub team. 
    }
    \label{fig:number-anomalies}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/erroneous-forecasts.png}
    \caption{
    Number of forecasts marked as erroneous and removed. Forecasts that were in extremely poor agreement with the observed values were removed from the analysis according to the criteria shown in Table \ref{tab:erroneous}. 
    }
    \label{fig:erroneous-forecasts}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width = 1\textwidth]{../output/figures/different-relative-errors.png}
\caption{Numerical comparison of different measures of relative error: absolute percentage error (APE), relative error (RE), symmetric absolute percentage error (SAPE) and the absolute error applied to log-transformed predictions and observations. We denote the predicted value by $\hat{y}$ and display errors as a function of the ratio of observed and predicted value. A: x-axis shown on a linear scale. B: x-axis shown on a logarithmic scale.}
\label{fig:SAPE}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{../output/figures/SIM-mean-state-size.png}
    \caption{Expected CRPS scores as a function of the mean and variance of the forecast quantity. We computed expected CRPS values  for three different distributions, assuming an ideal forecaster with predictive distribution equal to the true underlying (data-generating) distribution. 
    These expected CRPS values were computed for different predictive means based on 10,000 samples each and are represented by dots. Solid lines show the corresponding approximations of the expected CRPS from equations \eqref{eq:taylor_quadratic} and \eqref{eq:taylor_linear}. Figure \ref{fig:score-approx} shows the quality of the approximation in more detail. 
    The first distribution (red) is a truncated normal distribution with constant variance (we chose $\sigma = 1$ in order to only obtain positive samples). The second (green) is a negative binomial distribution with variance $\theta = 10$ and variance $\sigma^2 = \mu + 0.1\mu^2$. The third (blue) is a
    Poisson distribution with $\sigma^2 = \mu$. To make the scores for the different distributions comparable, scores were normalised to one, meaning that the mean score for every distribution (red, green, blue) is one. 
    A: Normalised expected CRPS for ideal forecasts with increasing means for three distribution with different relationships between mean and variance. Expected CRPS was computed on the natural scale (left), after applying a square-root transformation (middle), and after adding one and applying a log-transformation to the data (right). B: A but with x and y axes on the log scale.}
    \label{fig:SIM-wis-state-size-mean}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width = 1\textwidth]{../output/figures/illustration-effect-log-ranking-crps.png}
\caption{Illustration of the effect of the log-transformation of the ranking for a single forecast. Shown are CRPS (or WIS, respectively) values as a function of the observed value for two forecasters. Model A issues a geometric distribution (a negative binomial distribution with size parameter $\theta = 1$) with mean $\mu = 10$ and variance $\sigma^2 = \mu + \mu^2 = 110$), while Model B issues a Poisson distribution with mean and variance equal to 10. Zeroes in this illustrative example were handled by adding one before applying the natural logarithm.}
\label{fig:illustration-ranking}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{../output/figures/HUB-model-comparison-ensemble.png}
    \caption{
    Forecasts and scores for two-week-ahead predictions from the EuroCOVIDhub-ensemble made in Germany. Missing values are due to data anomalies that were removed (see section \ref{sec:HUB-setting}. 
    A, E: 50\% and 90\% prediction intervals and observed values for cases and deaths on the natural scale. B, F: Corresponding scores. C, G: Forecasts and observations on the log scale. D, H: Corresponding scores. 
    }
    \label{fig:HUB-model-comparison-ensemble}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{../output/figures/HUB-mean-obs-location.png}
    \caption{Observations and scores across locations and forecast horizons for the European COVID-19 Forecast Hub data. Locations are sorted according to the mean observed value in that location. 
    A: Average (across all time points) of observed cases and deaths for different locations. B: Corresponding boxplot (y-axis on log-scale) of all cases and deaths. C: Scores for two-week-ahead forecasts from the EuroCOVIDhub-ensemble (averaged across all forecast dates) for different locations, evaluated on the natural scale as well as after transforming counts by adding one and applying the natural logarithm. D: Corresponding boxplots of all individual scores of the EuroCOVIDhub-ensemble for two-week-ahead predictions. E: Boxplots for the relative change of scores for the EuroCOVIDhub-ensemble across forecast horizons. For any given forecast date and location, forecasts were made for four different forecast horizons, resulting in four scores. All scores were divided by the score for forecast horizon one. To enhance interpretability, the range of visible relative changes in scores (relative to horizon = 1) was restricted to [0.1, 10].}
    \label{fig:HUB-mean-locations}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{../output/figures/HUB-scores-locations-log-variants.png}
    \caption{Mean WIS in different locations for different transformations applied before scoring. Locations are sorted according to the mean observed value in that location. Shown are scores for two-week-ahead forecasts of the EuroCOVIDhub-ensemble. On the natural scale (with no transformation prior to applying the WIS), scores correlate strongly with the average number of observed values in a given location. The same is true for scores obtained after applying a square-root transformation, or after applying a log-transformation with a large offset $a$. For illustrative purposes, $a$ was chosen to be 101630 for cases and 530 for deaths, 10 times the respective median observed value. For large values of $a$, $\log(x + a)$ grows roughly linearly in $x$, meaning that we expect to observe the same patterns as in the case with no transformation. For decreasing values of $a$, we give more relative weight to scores in small locations.}
    \label{fig:HUB-log-different-offsets}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{../output/figures/HUB-transformation-regression.png}
    \caption{Relationship between median forecasts and scores. Black dots represent WIS values for two-week ahead predictions of the EuroCOVIDhub-ensemble. Shown in red are the regression lines discussed in Section \ref{sec:HUB-regression} shown in Table \ref{tab:HUB-regression}. A: WIS for two-week-ahead predictions of the EuroCOVIDhub-ensemble against median predicted values. B: Same as A, with scores obtained after applying a square-root-transformation to the data. C: Same as A, with scores obtained after applying a log-transformation to the data.} 
    \label{fig:HUB-regression}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{../output/figures/HUB-correlations.png}
    \caption{Correlations of rankings on the natural and logarithmic scale. A: Average Spearman rank correlation of scores for individual forecasts. For every individual target (defined by a combination of forecast date, target type, horizon, location), one score was obtained per model. Then, for every forecast target, the Spearman rank correlation was computed between scores on the natural scale and on the log scale for all the models that had made a forecast for that specific target. These individual rank correlations were then averaged across locations and time and are displayed stratified by horizon and target types, representing average accordance of model ranks for a single forecast target on the natural and on the log scale. B: Correlation between relative skill scores. For every forecast horizon and target type, a separate relative skill score was computed per model using pairwise comparisons, which is a measure of performance of a model relative to the others for a given horizon and target type that accounts for missing values. The plot shows the correlation between the relative skill scores on the natural vs. on the log scale, representing accordance of overall model performance as judged by scores on the natural and on the log scale.}
    \label{fig:HUB-cors}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{../output/figures/HUB-pairwise-comparisons.png}
    \caption{Changes in model ratings as measured by relative skill for two-week-ahead predictions for cases (top row) and deaths (bottom row). A: Relative skill scores for case forecasts from different models submitted to the European COVID-19 Forecast Hub computed on the natural scale. B: Change in rankings as determined by relative skill scores when moving from an evaluation on the natural scale to one on the logarithmic scale. Red arrows indicate that the relative skill score deteriorated when moving from the natural to the log scale, green arrows indicate they improved. C: Relative skill scores based on scores on the log scale. D: Difference in relative skill scores computed on the natural and on the logarithmic scale, ordered as in C. E: Relative contributions of the different WIS components (overprediction, underprediction, and dispersion) to overall model scores on the natural and the logarithmic scale. F, G, H, I, J, K: Analogously for deaths.}
    \label{fig:HUB-rank-order}
\end{figure}

@@

\paragraph{S1 Text.}
\label{sec:alternative-wis}
\textbf{Alternative Formulation of the WIS.}

\paragraph{S1 Figure.}
\label{fig:log-improper}
\textbf{Illustration of the effect of applying a transformation after scoring. }
We assume $Y \sim \text{LogNormal}(0, 1)$ and evaluate the expected CRPS for predictive distributions $\text{LogNormal}(0, \sigma)$ with varying values of $\sigma \in [0.1, 2]$. For the regular CRPS (left) and CRPS applied to log-transformed outcomes (middle), the lowest expectation is achieved for the true value $\sigma = 1$. For the log-transformed CRPS, the optimal value is  0.9, i.e. there is an incentive to report a forecast that is too sharp. The score is therefore no longer proper.

\paragraph{S2 Figure.}
\label{fig:illustration-effect-log-offset}
\textbf{Illustration of the effect of adding a small quantity to a value before taking the natural logarithm. }
For increasing x, all lines eventually approach the black line (representing a transformation with no offset applied).
    For a given solid line, the dashed line of the same colour marks the x-value that  is equal to 5 times the corresponding offset. It can be seen that for $a$ values smaller than one fifth of the transformed quantity, the effect of adding an offset is generally small. When choosing a suitable $a$, the trade-off is between staying close to the interpretation of a pure log-transformation (choosing a small $a$) and not giving excessive weights to small observations (by choosing a larger $a$, see Figure \ref{fig:HUB-log-different-offsets}).

\paragraph{S3 Figure.}
\label{fig:score-approx}
\textbf{Visualisation of expected CRPS values against approximated scores.} 
This is using the approximation detailed in Section \ref{sec:methods:rankings} (see also Figure \ref{fig:SIM-wis-state-size-mean}). Expected CRPS scores are shown for three different distributions once on the natural scale (top row) and once scored on the log scale (bottom row).

\paragraph{S1 Table.}
\label{tab:HUB-summary}
\textbf{Summary statistics for observations and scores for forecasts from the ECDC data set.}

\paragraph{S4 Figure.}
\label{fig:HUB-num-avail-models}
\textbf{Number of forecasts available from different models for each forecast date.}

\paragraph{S5 Figure.}
\label{fig:number-anomalies}
\textbf{Number of observed values that were removed as anomalous. }
The values were marked as anomalous by the European Forecast Hub team.

\paragraph{S6 Figure.}
\label{fig:erroneous-forecasts}
\textbf{Number of forecasts marked as erroneous and removed. } 
Forecasts that were in extremely poor agreement with the observed values were removed from the analysis according to the criteria shown in Table \ref{tab:erroneous}.

\paragraph{S2 Table.}
\label{tab:erroneous}
\textbf{Criteria for removing forecasts. }
Any forecast that met one of the listed criteria (represented by a row in the table), was removed. Those forecasts were removed in order to be better able to illustrate the effects of the log-transformation on scores and eliminating distortions caused by outlier forecasters. When evaluating models against each other (rather than illustrating the effect of a transformation), one would prefer not to condition on the outcome when deciding whether a forecast should be taken into account.

\paragraph{S7 Figure.}
\label{fig:HUB-model-comparison-baseline}
\textbf{Forecasts and scores for two-week-ahead predictions from the EuroCOVIDhub-baseline made in Germany. }
The model had zero included in some of its 50 percent intervals (e.g. for case forecasts in July 2021), leading to excessive dispersion values on the log scale. One could argue that including zero in the prediction intervals constituted an unreasonable forecast that was rightly penalised, but in general care has to be taken with small numbers. One potential way to do deal with this could be to use a higher $a$ value when applying a transformation $\log(x + a)$, for example $a = 10$ instead of $a = 1$. A, E: 50\% and 90\% prediction intervals and observed values for cases and deaths on the natural scale. B, F: Corresponding scores. C, G: Forecasts and observations on the log scale. D, H: Corresponding scores.

\paragraph{S8 Figure.}
\label{fig:HUB-model-comparison-epinow}
\textbf{Forecasts and scores for two-week-ahead predictions from the epiforecasts-EpiNow2 model made in Germany.} 
A, E: 50\% and 90\% prediction intervals and observed values for cases and deaths on the natural scale from the EpiNow2 model \citep{epinow2}. B, F: Corresponding scores. C, G: Forecasts and observations on the log scale. D, H: Corresponding scores.

\clearpage
\bibliography{../bib/log-or-not-v2.bib, ../bib/log-or-not.bib, ../bib/software.bib}
